---
title: "P8105 Homework1"
output: github_document
---

# Problem 1

***Dowloading Penguins dataset***

```{r}

data("penguins", package = "palmerpenguins")

```

***Code to inspect penguins dataset***

_Displays Data Frame_
```{r frame, eval= FALSE}

penguins

```

_Provides improtant summary information for our dataset_
```{r cool_sum, eval= FALSE}

skimr::skim(penguins)

```

_Gives number of rows in our dataset_
```{r row, eval= FALSE}

nrow(penguins)

```

_Gives number of columns in our dataset_
```{r col, eval= FALSE}

ncol(penguins)

```

_Code for getting mean flipper length_
```{r mean_flip, eval= FALSE}

mean(penguins$flipper_length_mm, na.rm = TRUE)

```
_The Penguins dataset has 8 columns and 344 rows. Important variables include penguin bill length, bill depth, flipper length, body mass and year. The flipper length of penguins in this datset is 200.9152. Other Important Characteristics: Mean Bill Length: 43.9, Mean Bill Depth: 17.2, Mean Body Mass (g): 4202_

***Creating Scatterplot Using GGplot***

Loading Tidyverse

```{r tidy}

library(tidyverse)

```

Creating Plot

```{r plot, warning= FALSE, }

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

```

```{r, echo = FALSE}

ggsave("bill_flipper_hw1_plot.pdf", height = 4, width = 6)

```

# Problem 2

_Creating Dataframe_

```{r tibble}

prb2_df <- tibble(
  norm_dist = rnorm(10),
  gt0 = norm_dist >= 0,
  vec_char <- c("evidence", "information", "input", "knowledge",    "picture", "statistics", "notes", "details", "reports",           "score"),
  vec_factor <-factor(c("Warm", "Hot", "Cold", "Cold", "Hot",       "Cold", "Cold", "Warm", "Cold", "Hot")))

```

_Displaying Dataframe_
  
```{r}

  prb2_df

```

 ***_Taking Means of Variables_***
 
 ```{r}
 
 mean(prb2_df$norm_dist)
 
 ```
 Taking mean of normal distribution works
 
  ```{r}
 
 mean(prb2_df$gt0)
 
 ```
 Taking mean of Boolean vector works
 
  ```{r}
 
 mean(prb2_df$vec_char)
 
 ```
 Taking mean of character vector does not work
 
  ```{r}
 
 mean(prb2_df$vec_factor)
 
 ```
 Taking mean of factor vector does not work
 
 ***Only numeric and logical variables work***
 
 ***Converting variable types***
 
 _Does Work_
 ```{r convert}
 
 as.numeric(prb2_df$gt0)
 
 ```
 
 _Does not Work_
  ```{r}
 
 as.numeric(prb2_df$vec_char)
 
 ```
When running this code for character/factor variables, you get the above message. Numeric(0) hints that there are no numeric values that can be converted
 
 

